Allocation Removal by Partial Evaluation in a Tracing JIT

### 2010-11-18 talk/pepm2011/paper.tex
next review comment

If one specific guard fails often enough\reva{when is that?}, the tracing JIT will generate a new
trace that starts exactly at the position of the failing guard
\cite{andreas_gal_incremental_2006}. The existing assembler is patched to jump
to the new trace when the guard fails.  This approach guarantees that all the
hot paths in the program will eventually be traced and compiled into efficient
code.

>>>>

If one specific guard fails a lot (\ie more than some threshold), the tracing JIT will generate a new
trace that starts exactly at the position of the failing guard
\cite{andreas_gal_incremental_2006}. The existing assembler is patched to jump
to the new trace when the guard fails.  This approach guarantees that all the
hot paths in the program will eventually be traced and compiled into efficient
code.
